---
title: "Munyo and Rossi (2015)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Munyo and Rossi (2015)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rART)
set.seed(123)
data("mr2015")
```

This example is from Section 4.2 of "A User's Guide to Approximate Randomization Tests with a Small Number of Clusters". The example is a replication of Munyo and Rossi (2015) which studies criminal recidivism of former prisoners by looking at the relationship between the number of inmates released from incarceration on a given day and the number of offenses committed on the same day.

# Make clusters

We start by making time based pseudo-clusters. The number of pseudo-clusters is at the digression of the analyst. We generate clusers according to the following table

```{r}
nr <- nrow(mr2015)
cluster_counts <- c(8,10,16)

knitr::kable(cbind(
  "# of Clusters (q)" = cluster_counts,
  "Cluster Size" = sapply(cluster_counts, function(q){floor(nr/q)})
))
```

with the remainder thrown into the last cluster. We first generate the cluster vectors and add them to the data frame. 

```{r}
makecluster <- function(q, n)
{
  cs <- floor(n/q); # cluster size
  cluster <- rep(1:q, each = cs)
  cluster <- c(cluster, rep.int(q, n-(cs*q))) # add remainder to cluster q
  cluster
}

# get a matrix of cluster data
clustercol <- vapply(cluster_counts, makecluster, numeric(nr), n = nr)

# make names for the clusters
(clnames <- paste("clusters", cluster_counts, sep = ""))

# append data to mr2015
mr2015[clnames] <- clustercol
```

# Regressions

We start with the first specification as it is the simplest. 

## Specification 1

We run it once for each set of clusters.

```{r}
sp1 <- formula(
  totalcrime ~ releases + temperature + rainfall + holiday + sunshine + 
    dayofweek + endofyear + year
)

sp1q8  <- artlm(sp1, cluster = clusters8,  data = mr2015, select = "releases")
sp1q10 <- artlm(sp1, cluster = clusters10, data = mr2015, select = "releases")
sp1q16 <- artlm(sp1, cluster = clusters16, data = mr2015, select = "releases")
```

We can get the p-values using `summary`

```{r}
(su11 <- summary(sp1q8))
(su12 <- summary(sp1q10))
(su13 <- summary(sp1q16))
```

and the confidence intervals using `confint`.

```{r}
(ci11 <- confint(sp1q8))
(ci12 <- confint(sp1q10))
(ci13 <- confint(sp1q16))
```

Note that the numbers are exactly the same as in the paper for `q = 8` and `q = 10`. However, they differ slightly for `q = 16`. This is because the function uses random sampling when the number of clusters exceeds 10.

## Other specifications

We already stored the results from the first specification. So, we don't need to compute it again. In this section, we will just output a table of all specifications to show that the results are the same. These are the other four specifications.

```{r}
specifications <- list(
  formula(
  totalcrime ~ releases + temperature + rainfall + holiday + sunshine + 
    dayofweek + endofyear + index
  ),
  formula(
  totalcrime ~ releases + temperature + rainfall + holiday + sunshine + 
    dayofweek + endofyear + month
  ),
  formula(
  totalcrime ~ releases + temperature + rainfall + holiday + sunshine + 
    dayofweek + endofyear + date + factor(year)*factor(month)
  ),
  formula(
  totalcrime ~ releases + temperature + rainfall + holiday + sunshine + 
    dayofweek + endofyear + factor(year)*factor(month)
  )
)
```

```{r}
(sp_num <- length(specifications))
(cl_num <- length(clnames))
```

```{r}
# initialize empty list
spregs <- list()

# create a call with common elements
fcall <- call("artlm", data = substitute(mr2015), select = "releases")

for (si in 1:sp_num) {
  for (ci in 1:cl_num){
    lcall <- fcall
    lcall$formula <- specifications[[si]]
    lcall$cluster <- as.name(clnames[ci])
    
    # number of the current iteration
    i <- cl_num*(si-1)+ci
    
    # add evaluated model to the list
    spregs[[i]] <- eval(lcall)
    
    # name the model
    names(spregs)[i] <- paste("s", (si+1), "c", ci, sep = "")
  }
}
```




